Results Analysis

### 2024-10-23 analysis/resultsAnalysis.Rmd
Updated via the Open Science Framework

---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  pdf_document: default
  html_document: default
---

@@

Remove excluded journals and create separate tibbles for prominent and randomly selected journals
```{r}
dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```
```{r}
# Run a test to ensure all randomly-selected and non-empirical journals removed from dj_prominent
assert_that(
  all(dj_prominent$sample_id == "prominent" | dj_prominent$sample_id == "both" 
      & dj_prominent$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

# Run a test to ensure all prominent sample and non-empirical journals removed from dj_random
assert_that(
  all(dj_random$sample_id == "random" | 
        dj_random$sample_id == "both" 
      & dj_random$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

@@

prominentCategory
```
Random journals Web Of Science categories
```{r}
randomCategory <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(field) %>%
  summarise(count = n()) %>%
  ungroup()

@@

Inspect how frequently PPC policies were stated for prominent journals 
```{r}
prominentPPC <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

prominentPPC
```
Get the names of the prominent journals that have 'NO EXPLICIT' PPC options
```{r}
dj_prominent %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```
Get names for prominent journals that offered more than one type of PPC
```{r}
# Return count
dj_prominent %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

Inspect PPC types at prominent journals
```{r}
table(dj_prominent$ppc_name)
```
Inspect the COPE status of prominent journals with and without PPC policies
```{r}
promCOPE <- dj_prominent %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

promCOPE
```

Inspect how frequently PPC policies were stated for randomly selected journals 
```{r}
randomPPC <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

randomPPC
```
Get the names of the randomly selected journals that have 'NO EXPLICIT' PPC options
```{r}
dj_random %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

@@

@@

#CIs for 'Yes Explicit'
randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)

randomPPC_CI
```
Get names for randomly selected journals that offered more than one type of PPC
```{r}
# Return all rows with ppc_name values for ppc_type B and C
dj_random %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

@@

```{r}
# Peer review statistics by types
prominentReviewAll <- dj_prominent %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)
  ) %>%
  ungroup()

@@

randomReviewAll

```{r}
# Peer review statistics by types
randomReviewAll <- dj_random %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)
  ) %>%
  ungroup()

randomReviewAll
```
# STUDY 2: PREVALENCE

@@

Look for instances of PPC in articles published in prominent journals
```{r}
d_articles %>%
  filter(sample_id == "prominent",
         exclude_reason == "IS ITSELF PPC") %>%
  summarise(n = n())
```
Calculate CIs for Instance PPC in prominent journals
```{r}
# Instance PPCs
prominent_instance <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "prominent",
    exclude_reason == "IS ITSELF PPC") %>%
  count()

@@

ci_promInstance_LL
ci_promIinstance_UL
```
Look for linked PPC in articles in random sample
```{r}
d_articles %>%
  filter(sample_id == "random",
         ppc_linked == TRUE) %>%
  summarise(n = n())
```

@@

ci_randLinked_LL
ci_randLinked_UL
```
Look for instances of PPC in articles in random sample
```{r}
d_articles %>%
  filter(sample_id == "random",
         exclude_reason == "IS ITSELF PPC") %>%
  summarise(n = n())
```

@@

# FIGURES
Boxplot of quantitative length limits
```{r}
quantLength <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_length),
         ppc_length != "NOT STATED",
         ppc_length != "Qualitative") %>%
 mutate(Length = as.numeric(ppc_length))

@@

ggsave("lengthLimits.png", plot = last_plot(), device = "png")
```
Boxplot of quantitative time limits
```{r}
quantTime <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_time),
         ppc_time != "NOT STATED",
         ppc_time != "Qualitative") %>%
 mutate(Time = as.numeric(ppc_time))

@@

ggsave("timeLimits.png", plot = last_plot(), device = "png")
```
### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*

```{r, echo = FALSE, message=FALSE}
# Filter and transform restrictions for ppc_length
prominent_length_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>% 
  group_by(ppc_length) %>%
  summarise(count = n())

>>>>

---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  html_document: default
---

@@

Remove excluded, non-empirical, journals and create separate tibbles for prominent and randomly selected journals
```{r}
dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```
Run assertion checks for both samples
```{r}
# Check all randomly-selected and non-empirical journals have been removed from dj_prominent
assert_that(
  all(dj_prominent$sample_id == "prominent" | dj_prominent$sample_id == "both" 
      & dj_prominent$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

# Check all prominent sample and non-empirical journals have been removed from dj_random
assert_that(
  all(dj_random$sample_id == "random" | 
        dj_random$sample_id == "both" 
      & dj_random$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

@@

prominentCategory
```

Random journals Web Of Science categories
```{r}
randomCategory <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(field) %>%
  summarise(count = n()) %>%
  ungroup()

@@

PROMINENT SAMPLE
Inspect how frequently PPC policies were stated for prominent journals 
```{r}
prominentPPC <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

prominentPPC
```

Get the names of the prominent journals that have 'NO EXPLICIT' PPC options
```{r}
dj_prominent %>%
  filter(ppc_type == "A" & has_ppc == "NO EXPLICIT") %>%
  print()
```

Get names for prominent journals that offered more than one type of PPC
```{r}
# Return count
dj_prominent %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

Inspect PPC types at prominent journals
```{r}
table(dj_prominent$ppc_name)
```

Inspect the COPE status of prominent journals with and without PPC policies
```{r}
promCOPE <- dj_prominent %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercentage = round((COPE_count / total_count) * 100)) %>%
 ungroup()

promCOPE
```
RANDOMLY-SELECTED SAMPLE
Inspect how frequently PPC policies were stated for randomly selected journals 
```{r}
randomPPC <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

randomPPC
```

@@

randomPPCno <- dj_random %>%
  filter(ppc_type == 'A', is.na(ppc_name)) %>%
  summarise(count = n())

@@

# CIs for 'Yes Explicit'
randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)

# CIs for 'No' (both explicit and Implicit)
randomPPC_CI_neg <- binom.confint(randomPPCno, sample_size, method = "wilson", conf.level = confidence_level)

# View results
randomPPC_CI
randomPPC_CI_neg
```
*Note.* CIs were not calculated for the prominent sample of journals as they represented our entire population of interest.

Get names for randomly selected journals that offered more than one type of PPC
```{r}
# Return all rows with ppc_name values for ppc_type B and C
dj_random %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) %>%
  print()
```

@@

```{r}
# Peer review statistics by types
prominentReviewType <- dj_prominent %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)
  ) %>%
  ungroup()

prominentReviewType
```

@@

randomReviewAll
```

```{r}
# Peer review statistics by types
randomReviewType <- dj_random %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  group_by(ppc_name) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)
  ) %>%
  ungroup()

randomReviewType
```

# STUDY 2: PREVALENCE

@@

Look for instances of PPC in articles published in prominent journals
```{r}
d_articles %>%
  filter(sample_id == "prominent",
         exclude_reason == "IS ITSELF PPC") %>%
  summarise(n = n())
```

Calculate CIs for Instance PPC in prominent journals
```{r}
# Instance PPCs
prominent_instance <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "prominent",
    exclude_reason == "IS ITSELF PPC") %>%
  count()

@@

ci_promInstance_LL
ci_promIinstance_UL
```

Look for linked PPC in articles in random sample
```{r}
d_articles %>%
  filter(sample_id == "random",
         ppc_linked == TRUE) %>%
  summarise(n = n())
```

@@

ci_randLinked_LL
ci_randLinked_UL
```

Look for instances of PPC in articles in random sample
```{r}
d_articles %>%
  filter(sample_id == "random",
         exclude_reason == "IS ITSELF PPC") %>%
  summarise(n = n())
```

@@

# FIGURES
*Note.* These figures are not included in the final article as they do not offer additional informative informative beyond what was reported in the tables.

Boxplot of quantitative length limits
```{r}
quantLength <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_length),
         ppc_length != "NOT STATED",
         ppc_length != "Qualitative") %>%
 mutate(Length = as.numeric(ppc_length))

@@

ggsave("lengthLimits.png", plot = last_plot(), device = "png")
```

Boxplot of quantitative time limits
```{r}
quantTime <- d_journals %>%
 select(c(sample_id, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_time),
         ppc_time != "NOT STATED",
         ppc_time != "Qualitative") %>%
 mutate(Time = as.numeric(ppc_time))

@@

ggsave("timeLimits.png", plot = last_plot(), device = "png")
```

### *Post-Publication Critique Policy and Restriction Statements in Prominent Psychology Journals*
```{r, echo = FALSE, message=FALSE}
# Filter and transform restrictions for ppc_length
prominent_length_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>% # removes 'Archive Only' PPC types
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>% 
  group_by(ppc_length) %>%
  summarise(count = n())
